Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-08 prop_iop.tex
prop_iop.tex Rename to follow the guideline...
Rename the figures according to the guild line...
prop_iop.tex Updated until the Guildline section 4...

\begin{document}
\title{Measurement and Probability in Fuzzy Quantum Theories}
\date{\today}
\maketitle

@@

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed. In a strict computational
or experimental setting, one should question the reliance of the
definition of probability space on the uncountable and
uncomputable real
interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
This interval includes numbers like
$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\frac{\pi}{4}$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

@@

In the previous example, we assumed the probability~$\pmeas(E)$ of
each event~$E$ is known a priori. In reality, although each event is
assumed to have a probability, the exact value of $\pmeas(E)$ may not
be known. According to the \emph{frequency interpretation of
  probability} (which we will revisit when moving to the quantum
case)~\cite{Venn1876,Hajek2012}, 
to determine the probability of an event, we run $M$
independent trials which gives us an approximation of the (assumed)
``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
whether the event~$E$ occurs in the $i$-th trial or not, then
$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
the relative frequency~$\frac{1}{M}\sum_{i=1}^{M}x_{i}$ with the
probability converging to one as $M$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

\noindent It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an interval-valued
measure using arbitrary small intervals as discussed in appendix~\ref{sec:Real-and-Interval}.
However, to simplify our discussion, we will focus on only three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\begin{equation}
\iota(x)=\cases{
\necess & if $x=1$ ;\\
\imposs & if $x=0$ ;\\
\unknown & otherwise.
}\label{eq:homomorphism}
\end{equation}
For example, Fig.~\ref{fig:three-dimensional-3-value} plots the
1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given a quantum interval-valued probability measure, i.e., given observations
done with finite resources. In the case the intervals are infinitely
precise the question reduces to Gleason's theorem which states that
the state of the quantum system is uniquely determined by the probability
measure. But surely the less resources are available, the less precise
the intervals, and the less we expect to know about the state of the
system. To formally state and answer this question we begin with defining
the \emph{core} and \emph{convexity} of a probability measure as follows.
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{measure3} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{measure4.pdf}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
\end{figure}

@@

\begin{example}[Three-dimensional quantum four-interval-valued 
  probability measure]\label{ex:three-dimensional-4-value}
  Given a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
  }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
  $\ket{\minus}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
  $\bar{\mu}$ below refers to Fig.~\ref{fig:three-dimensional-4-value}
  which plots the 1-dimensional projectors:
\begin{enumerate}
\item Let:
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) 
  &=& \imposs \\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) 
  &=& \necess
\end{eqnarray*}
where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
vectors, respectively.
\item The red and green circles are are the states orthogonal to
  $\ket{0}$ and $\ket{\ps}$, respectively, and can be parametrized as
  $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
  and
  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\minus}+\cos\theta\ket{2}$,
  where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
  half of those states need special treatment, i.e., whenever
  $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)
  &=& \likely \\
\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) 
  &=& \unlikely
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
\end{enumerate}
It is straightforward but tedious to check that $\bar{\mu}$ is a
quantum interval-valued probability measure. Although we have not
verified that $\bar{\mu}$ is convex, the following argument establishes
that is has an empty core. Assume there is a real-valued probability
measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]
This measure however is ``better'' than the previous one in the
sense that it might only be induced by $\ket{2}$ or the density matrix
$\frac{\mathbb{1}}{3}$, but not by $\ket{1}$. \end{example}

In general, each two 1-dimensional projectors~$\proj{\psi_{0}}$
and $\proj{\psi_{1}}$ mapping to $\imposs$ suggests $\bar{\mu}$
might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
in the Hilbert space of dimension 3. As we illustrated in figure~\ref{fig:three-dimensional-3-value},
if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
is contained in a plane, which contains no area in the sphere. On
the other hand, if the states mapping to $\imposs$ contain some area
in the sphere as in figure~\ref{fig:three-dimensional-3-value-1},
each plane intersecting the area suggests different pure state inducing
$\bar{\mu}$. However, these suggestions contradict with each others,
which implies $\bar{\mu}$ has an empty core. Furthermore, the larger
the area, the more state vectors which are inconsistent with any particular
Born rule probability measure. Therefore, the area of the 1-dimensional
projectors mapping to $\imposs$ could indicate how much $\bar{\mu}$
deviate from the Born rule probability measures.
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{measure3-1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value-1}Plotted in $\mathbb{R}^{3}$,
assume the 1-dimensional projectors whose latitude is higher than
the green circle maps to $\imposs$ by $\bar{\mu}$, for example $\bar{\mu}\left(\proj{0'}\right)=\bar{\mu}\left(\proj{2'}\right)=\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$.
Since $\ket{0'}$ and $\ket{2'}$ are in a plane, $\bar{\mu}$ might
be induced by its normal vector~$\ket{1'}$. Also, since $\ket{0'}$
and $\ket{\bar{2}}$ are in a plane, $\bar{\mu}$ might be induced
by its normal vector~$\ket{\bar{1}}$. However, $\mu_{\ket{1'}}^{B}$
is inconsistent with $\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$,
and $\mu_{\ket{\bar{1}}}^{B}$ is inconsistent with $\bar{\mu}\left(\proj{2'}\right)=\imposs$.
Therefore, $\bar{\mu}$ has an empty-core.}
\end{figure}

@@

\appendix

\section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}

@@

\section{Real Interval-valued Frame Functions\label{sec:Real-Interval-valued-Frame}}

@@

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$.\end{lemma}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{equation}
\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
}
\label{eq:includes}
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

@@

\section{Quantum and Classical Interval-valued Probability Measures}

@@

\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}

>>>>

\begin{document}
\title{Measurement and Probability in Fuzzy Quantum
Theories}

\author{Andrew J Hanson$^{1}$, Gerardo Ortiz$^{2}$,
Amr Sabry$^{1}$ and Yu-Tsung Tai$^{3,1}$}
\address{$^{1}$ School of Informatics and Computing, Indiana
University, Bloomington, IN 47405, USA}
\address{$^{2}$ Department of Physics, Indiana University, Bloomington, IN
47405, USA}
\address{$^{3}$ Department of Mathematics, Indiana University, Bloomington,
IN 47405, USA}
\ead{ortizg@indiana.edu}
\begin{abstract}
\today
\end{abstract}
\pacs{03.65.-w, 03.65.Ta, 02.40.Dr, 02.50.Cw, 02.50.Le}
\noindent{\it Keywords\/}: {Finite precision measurement, the Born rule, Gleason's theorem, interval-valued
probability, discrete quantum theory}

\submitto{\jpa}

@@

\noindent It is useful to think that this probability measure is
completely determined by the ``reality'' of the two coins in question
and their characteristics, in the sense that each pair of coins
induces a measure, and each measure must correspond to some pair of
coins. The measure above would be induced by two particular coins such
that the first coin is twice as likely to land tails up than heads up
and the second coin is double-headed. In a strict computational
or experimental setting, one should question the reliance of the
definition of probability space on the uncountable and
uncomputable real
interval~$[0,1]$~\cite{Turing_1937,Ziegler2007,weihrauch2012computable}.
This interval includes numbers like
$0.h_{1}h_{2}h_{3}\ldots$ where $h_{i}$ is 1 or 0 depending on whether
Turing machine $\mathit{TM}_{i}$ halts or not. Such numbers cannot be
computed. This interval also includes numbers like $\pi / 4$
which can only be computed with increasingly large resources as the
precision increases. Therefore, in a resource-aware computational or
experimental setting, it is more appropriate to consider probability
measures that map events to a set of elements computable with a fixed
set of resources. We expand on this observation in the next section
and then recall its formalization using interval-valued probability
measures~\cite{Weichselberger2000,JamisonLodwick2004}.

@@

In the previous example, we assumed the probability~$\pmeas(E)$ of
each event~$E$ is known a priori. In reality, although each event is
assumed to have a probability, the exact value of $\pmeas(E)$ may not
be known. According to the \emph{frequency interpretation of
  probability} (which we will revisit when moving to the quantum
case)~\cite{Venn1876,Hajek2012}, 
to determine the probability of an event, we run $M$
independent trials which gives us an approximation of the (assumed)
``true'' or ``real'' probability. Let $x_{i}$ be 1 or 0 depending on
whether the event~$E$ occurs in the $i$-th trial or not, then
$\pmeas(E)$ could be approximated to given accuracy~$\epsilon>0$ by
the relative frequency~$\sum_{i=1}^{M}x_{i} / M$ with the
probability converging to one as $M$ goes to infinity, i.e.,
\[
\forall\epsilon>0,\lim_{M\rightarrow\infty}\pmeas\left(\left|\pmeas(E)-\frac{1}{M}\sum_{i=1}^{M} x_{i}\right|<\epsilon\right)=1\textrm{ .}
\]
This fact is called the law of large numbers~\cite{Bernoulli2006,Kolmogorov1950,Uspensky1937,Shafer1976,544199}.

@@

\noindent It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an interval-valued
measure using arbitrary small intervals as discussed in appendix~\ref{sec:Real-and-Interval}.
However, to simplify our discussion, we will focus on only three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Given a quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$,
we define a quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by $\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is defined by 
\begin{equation}
\iota(x)=\cases{
\necess & if $x=1$ ;\\
\imposs & if $x=0$ ;\\
\unknown & otherwise.
}\label{eq:homomorphism}
\end{equation}
For example, figure~\ref{fig:three-dimensional-3-value} plots the
1-dimensional projectors mapped by $\iota\left(\mu_{\ket{0}}^{B}(P)\right)$.
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given a quantum interval-valued probability measure, i.e., given observations
done with finite resources. In the case the intervals are infinitely
precise the question reduces to Gleason's theorem which states that
the state of the quantum system is uniquely determined by the probability
measure. But surely the less resources are available, the less precise
the intervals, and the less we expect to know about the state of the
system. To formally state and answer this question we begin with defining
the \emph{core} and \emph{convexity} of a probability measure as follows.
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figure1.eps} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value}This figure illustrates the
1-dimensional projectors mapped by $\bar{\mu}_{\ket{0}}^{B}(P)=\iota\left(\mu_{\ket{0}}^{B}(P)\right)$
plotted in $\mathbb{R}^{3}$. The red dotted vector is $\ket{0}$,
and $\bar{\mu}_{\ket{0}}^{B}\left(\proj{0}\right)=\necess$. $\ket{0}$
is the normal vector of the plane so that we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\imposs$
for any vector~$\ket{\psi}$ in the plane. For any other vector~$\ket{\psi}$,
we have $\bar{\mu}_{\ket{0}}^{B}\left(\proj{\psi}\right)=\unknown$.}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.38]{figure2.eps}
\end{center}
\caption{\label{fig:three-dimensional-4-value}This figure illustrates
  cases 1 and 2 of example~\ref{ex:three-dimensional-4-value} plotted
  in $\mathbb{R}^{3}$. The red and green dotted vectors are $\ket{0}$
  and $\ket{\ps}$ respectively.  All possible real vectors of the subspaces
  $\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps_{\theta,\gamma}^{\perp}}$ are drawn in the red and green
  circles, respectively. Within the circles, a dotted
  vector~$\ket{\psi}$ means $\bar{\mu}(\proj{\psi})=\likely$;
  otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$. The gray vector is a
  generic vector~$\ket{0_{\theta,\gamma}^{\perp}}$, and the red and
  green solid vectors are normalized
  $\ket{0}\times\ket{0_{\theta,\gamma}^{\perp}}$ and
  $\ket{\ps}\times\ket{0_{\theta,\gamma}^{\perp}}$, respectively, where
  $\times$ is the usual cross product in $\mathbb{R}^{3}$.}
\end{figure}

@@

\begin{example}[Three-dimensional quantum four-interval-valued 
  probability measure]\label{ex:three-dimensional-4-value}
  Given a three dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.  Let \emph{
  }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
  $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and
  $\ket{\minus}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$. The definition of
  $\bar{\mu}$ below refers to figure~\ref{fig:three-dimensional-4-value}
  which plots the 1-dimensional projectors:
\begin{enumerate}
\item Let:
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) 
  &=& \imposs \\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps}) 
  &=& \necess
\end{eqnarray*}
where $\ket{0}$ and $\ket{\ps}$ are plotted as the red and green dotted
vectors, respectively.
\item The red and green circles are are the states orthogonal to
  $\ket{0}$ and $\ket{\ps}$, respectively, and can be parametrized as
  $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
  and
  $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\minus}+\cos\theta\ket{2}$,
  where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
  half of those states need special treatment, i.e., whenever
  $0\le\theta<\frac{\pi}{2}$ and $0\le\gamma<\pi$, we define
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right)
  &=& \likely \\
\bar{\mu}\left(\mathbb{1}-\proj{0_{\theta,\gamma}^{\perp}}\right)=
  \bar{\mu}\left(\mathbb{1}-\proj{\ps_{\theta,\gamma}^{\perp}}\right) 
  &=& \unlikely
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}-\proj{\psi})=\likely$. 
\end{enumerate}
It is straightforward but tedious to check that $\bar{\mu}$ is a
quantum interval-valued probability measure. Although we have not
verified that $\bar{\mu}$ is convex, the following argument establishes
that is has an empty core. Assume there is a real-valued probability
measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$ for all $P\in\events$.
Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]
This measure however is ``better'' than the previous one in the
sense that it might only be induced by $\ket{2}$ or the density matrix
$\frac{\mathbb{1}}{3}$, but not by $\ket{1}$. \end{example}

In general, each two 1-dimensional projectors~$\proj{\psi_{0}}$
and $\proj{\psi_{1}}$ mapping to $\imposs$ suggests $\bar{\mu}$
might be induced by the pure state~$\ket{\psi_{0}}\times\ket{\psi_{1}}$
in the Hilbert space of dimension 3. As we illustrated in figure~\ref{fig:three-dimensional-3-value},
if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
is contained in a plane, which contains no area in the sphere. On
the other hand, if the states mapping to $\imposs$ contain some area
in the sphere as in figure~\ref{fig:three-dimensional-3-value-1},
each plane intersecting the area suggests different pure state inducing
$\bar{\mu}$. However, these suggestions contradict with each others,
which implies $\bar{\mu}$ has an empty core. Furthermore, the larger
the area, the more state vectors which are inconsistent with any particular
Born rule probability measure. Therefore, the area of the 1-dimensional
projectors mapping to $\imposs$ could indicate how much $\bar{\mu}$
deviate from the Born rule probability measures.
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figure3.eps} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value-1}Plotted in $\mathbb{R}^{3}$,
assume the 1-dimensional projectors whose latitude is higher than
the green circle maps to $\imposs$ by $\bar{\mu}$, for example $\bar{\mu}\left(\proj{0'}\right)=\bar{\mu}\left(\proj{2'}\right)=\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$.
Since $\ket{0'}$ and $\ket{2'}$ are in a plane, $\bar{\mu}$ might
be induced by its normal vector~$\ket{1'}$. Also, since $\ket{0'}$
and $\ket{\bar{2}}$ are in a plane, $\bar{\mu}$ might be induced
by its normal vector~$\ket{\bar{1}}$. However, $\mu_{\ket{1'}}^{B}$
is inconsistent with $\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$,
and $\mu_{\ket{\bar{1}}}^{B}$ is inconsistent with $\bar{\mu}\left(\proj{2'}\right)=\imposs$.
Therefore, $\bar{\mu}$ has an empty-core.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ack

Anyone who has discussed this with us?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Interval-valued Frame Functions\label{sec:Interval-valued-Frame-Functions}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real Interval-valued Frame Functions\label{sec:Real-Interval-valued-Frame}}

@@

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\frac{\pi}{2}-\theta_{0},\frac{\pi}{2}\right]\right)$.\end{lemma}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figureb1.eps} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{equation}
\eqalign{\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
}
\label{eq:includes}
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum and Classical Interval-valued Probability Measures}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantum Real-valued and Interval-valued Probability Measures\label{sec:Real-and-Interval}}
